---
title: "Example datasets recommender interface"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(Matrix)
library(shiny)
library(flexdashboard)
library(DT)
library(rmarkdown)
library(stopwords)
library(SnowballC)
library(purrr)
library(tidyverse)

library(OutlierIdentifiers)
library(SparseMatrixRecommender)
library(SMRMon)
library(LSAMon)
```

```{r get-data, include=FALSE}

load( file = "smrWLDatasets.RData" )
load( file = "lsaWLDatasetsWordsAndPhrases.RData" )
load( file = "dfWLExampleData.RData" )

load( file = "smrRDatasets.RData" )
load( file = "lsaRDatasetsWordsAndPhrases.RData" )
load( file = "dfRExampleData.RData" )

lsRecommenders <- list( "Mathematica" = smrWLDatasets,                "R" = smrRDatasets )
lsLSAObjects   <- list( "Mathematica" = lsaWLDatasetsWordsAndPhrases, "R" = lsaRDatasetsWordsAndPhrases )
lsData         <- list( "Mathematica" = dfWLExampleData,              "R" = dfRExampleData )

# lsRecommenders <- 
#   purrr::map( lsRecommenders, function(smr) {
#     smr %>% SMRMonApplyTermWeightFunctions( "None", "None", "Cosine" )
#   })
```

Parameters {.sidebar}
=======================================================================

```{r}
selectInput( inputId = "recommender", 
             label = "Type:", 
             choices = setNames( names(lsRecommenders), paste( names(lsRecommenders), "datasets" ) ), 
             selected = "R")
```


```{r}
smrObj <- 
  reactive({
    lsRecommenders[[ input$recommender ]]
  })

lsaObj <- 
  reactive({
    lsLSAObjects[[ input$recommender ]]
  })

dfData <- 
  reactive({
    lsData[[ input$recommender ]]
  })
```

```{r}
sliderInput( inputId = "numberOfRecs", label = "Number of recommendations:", min = 1, max = 300, value = 10, step = 1 )
```

```{r, echo=F}
uiOutput("dynamic")


output$dynamic <- renderUI({ 
  
  do.call( tagList,
          purrr::map( smrObj() %>% SMRMonTakeTagTypes, function(tt) {
            sliderInput( inputId = paste0( tt, "Weight"), label = paste0( tt, " weight:"), min = 0, max = 1, value = 1, step = 0.01 )
            })
          )

})
```

```{r}
tagTypeWeights <- 
  reactive(
    purrr::map_dbl( smrObj() %>% SMRMonTakeTagTypes, function(tt) { input[[ paste0( tt, "Weight") ]] }) 
  )
```


Recommendations
=======================================================================

Row {data-height=800}
-----------------------------------------------------------------------

### Tags

```{r}
textAreaInput( 
  inputId = "tagsText", 
  label = "Tag text (metadata)", 
  placeholder = "Package:dplyr, ColumnsCount:2, ColumnType:Character:0.5", 
  width = "600px", cols = 300, rows = 8 )

lsTagsProf <- 
  reactive({
    
    if( nchar(input$tagsText) == 0) { 
      NULL 
    } else {
      res <- trimws( strsplit(input$tagsText, split = ",")[[1]] )
      res <- res[ nchar(res) > 0 ]
      
      dfRes <- as.data.frame(stringr::str_split_fixed( string = res, pattern = ":", n = 3))
      
      dfRes[[3]] <- as.numeric(dfRes[[3]])
      dfRes[[3]][is.na(dfRes[[3]])] <- 1
      
      dfRes <- 
        purrr::map_df( split(dfRes,1:nrow(dfRes)), function(dfX) {
          data.frame( Tag = paste0( dfX[[1,1]], ":", dfX[[1,2]] ), Score = dfX[[1,3]] )
        })
      dfRes <- dfRes[ dfRes$Tag %in% colnames(smrObj()$M), ] 
      setNames( dfRes$Score, dfRes$Tag )
    }
  })
```

Known tags:

```{r}
renderText(paste(names(lsTagsProf()), collapse = ", "))
```

### Free text

```{r}
textAreaInput( 
  inputId = "freeText", 
  label = "Free text (description)", 
  placeholder = "Airline time series data", 
  width = "600px", cols = 300, rows = 8 )

lsFreeWordsProf <- 
  reactive({
    
    if( nchar(input$freeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTerms( query = input$freeText ) %>% 
        LSAMonTakeValue
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[abs(lsCSums) > 0]
      
      if( length(lsProf) > 0 ) { 
        names(lsProf) <- paste0( "Word:", names(lsProf) )
        lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
        
        if( max(abs(lsProf)) > 0 ) { lsProf <- lsProf / max(abs(lsProf)) }
        rev(sort(lsProf))
      } else {
        NULL
      }
    }
    
  })

lsFreeTopicsProf <- 
  reactive({
    
    if( nchar(input$freeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTopics( query = input$freeText ) %>% 
        LSAMonTakeValue
      
      matRes <- SMRApplyTermWeightFunctions( matRes, "None", "None", "Cosine" )
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[abs(lsCSums) > 0]
      
      if( length(lsProf) > 0 ) { 
        names(lsProf) <- paste0( "Topic:", names(lsProf) )
        lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
        
        if( max(abs(lsProf)) > 0 ) { lsProf <- lsProf / max(abs(lsProf)) }
        rev(sort(lsProf))
      } else {
        NULL
      }
    }
    
  })
```


Extracted words and topics:

```{r}
lsFreeProf <- reactive({ c( lsFreeWordsProf(), lsFreeTopicsProf() ) })
DT::renderDataTable(
  expr = data.frame( Word = names(lsFreeProf()), Score =  lsFreeProf() ),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
)
```

Row
-----------------------------------------------------------------------


### Recommendations with both tags and free text

```{r}
lsProf <- 
  reactive({ 
    c( 
      lsTagsProf(),
      lsFreeProf() 
    ) 
  })

DT::renderDataTable(
  if( is.null(lsProf()) || length(lsProf()) == 0 ) {
    NULL
  } else {
    smrObj() %>% 
      SMRMonApplyTagTypeWeights( 
        weights = tagTypeWeights(), 
        default = 1 ) %>% 
      SMRMonRecommendByProfile( profile = lsProf(), nrecs = input$numberOfRecs ) %>% 
      SMRMonJoinAcross( dfData() ) %>% 
      SMRMonTakeValue
    },
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```



Profiles
=======================================================================

Row {data-height=800}
-----------------------------------------------------------------------

### Items

```{r}
textAreaInput( inputId = "profileTagsText", 
               label = "Items text (points)", 
               placeholder = "dplyr-band_instruments",
               width = "600px", 
               cols = 300, rows = 8)

lsItemsHist <- 
  reactive({
    
    if( nchar(input$profileTagsText) == 0) { 
      NULL 
    } else {
      res <- trimws( strsplit(input$profileTagsText, split = ",")[[1]] )
      res <- res[ nchar(res) > 0 ]
      
      dfRes <- setNames( as.data.frame(stringr::str_split_fixed( string = res, pattern = ":", n = 2)), c("Item", "Rating"))
      
      dfRes[[2]] <- as.numeric(dfRes[[2]])
      dfRes[[2]][is.na(dfRes[[2]])] <- 1
      
      dfRes <- dfRes[ dfRes$Item %in% rownames(smrObj()$M), ] 
      setNames( dfRes$Rating, dfRes$Item )
    }
  })
```

Known items:

```{r}
renderText(paste(names(lsItemsHist()), collapse = ", "))
```

### Free text

```{r}
textAreaInput( 
  inputId = "profileFreeText", 
  label = "Free text (description)", 
  placeholder = "Airline time series data", 
  width = "600px", cols = 300, rows = 8 )

lsProfileFreeWordsProf <- 
  reactive({
    
    if( nchar(input$profileFreeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTerms( query = input$profileFreeText ) %>% 
        LSAMonTakeValue
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[abs(lsCSums) > 0]
      
      if( length(lsProf) > 0 ) { 
        names(lsProf) <- paste0( "Word:", names(lsProf) )
        lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
        
        if( max(abs(lsProf)) > 0 ) { lsProf <- lsProf / max(abs(lsProf)) }
        rev(sort(lsProf))
      } else {
        NULL
      }
    }
    
  })

lsProfileFreeTopicsProf <- 
  reactive({
    
    if( nchar(input$profileFreeText) == 0) { 
      NULL 
    } else {
      
      matRes <- 
        lsaObj() %>% 
        LSAMonRepresentByTopics( query = input$profileFreeText ) %>% 
        LSAMonTakeValue
      
      matRes <- SMRApplyTermWeightFunctions( matRes, "None", "None", "Cosine" )
      
      lsCSums <- colSums(matRes)
      lsProf <- lsCSums[abs(lsCSums) > 0]
      
      if( length(lsProf) > 0 ) { 
        names(lsProf) <- paste0( "Topic:", names(lsProf) )
        lsProf <- lsProf[ names(lsProf) %in% colnames(smrObj()$M) ]
        
        if( max(abs(lsProf)) > 0 ) { lsProf <- lsProf / max(abs(lsProf)) }
        rev(sort(lsProf))
      } else {
        NULL
      }
    }
    
  })

dfItemsByFreeText <- 
  reactive({
    if( is.null(lsProfileFreeProf()) || length(lsProfileFreeProf()) == 0) { 
      NULL
    } else {
      smrObj() %>% 
        SMRMonApplyTagTypeWeights( 
          weights = tagTypeWeights(),
          default = 1 ) %>% 
        SMRMonRecommendByProfile( profile = lsProfileFreeProf(), nrecs = input$numberOfRecs, normalizeQ = TRUE ) %>% 
        SMRMonTakeValue
    }
  })
    
dfProfileByFreeText <- 
  reactive({
    if( is.null(dfItemsByFreeText()) || nrow(dfItemsByFreeText()) == 0) { 
      NULL
    } else {
      smrObj() %>% 
        SMRMonProfile( history = setNames(dfItemsByFreeText(), c("Rating", "Index", "Item")), tagTypesQ = TRUE, normalizeQ = TRUE ) %>% 
        SMRMonTakeValue
    }
  })
```


Extracted words and topics:

```{r}
lsProfileFreeProf <- reactive({ c( lsProfileFreeWordsProf(), lsProfileFreeTopicsProf() ) })
DT::renderDataTable(
  expr = data.frame( Word = names(lsProfileFreeProf()), Score =  lsProfileFreeProf() ),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
)
```


Row
-----------------------------------------------------------------------

### Profile of items

```{r}
dfProfileByItemsHist <- 
  reactive({
    if( is.null(lsItemsHist()) || length(lsItemsHist()) == 0) { 
      NULL
    } else {
      smrObj() %>%     
        SMRMonApplyTagTypeWeights( 
          weights = tagTypeWeights(), 
          default = 1 ) %>% 
        SMRMonProfile( history = lsItemsHist(), tagTypesQ = TRUE, normalizeQ = TRUE ) %>% 
        SMRMonTakeValue
    }
  })
```

```{r}
DT::renderDataTable( dfProfileByItemsHist(),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```


### Profile by free text

```{r}
DT::renderDataTable(
  dfProfileByFreeText(),
  options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```


### Profile by both items and free text

```{r}

DT::renderDataTable({
  if( is.null( dfProfileByItemsHist()) && is.null( dfProfileByFreeText() ) ) {
    NULL
  } else {
    dfProf <- rbind( dfProfileByItemsHist(), dfProfileByFreeText() )
    if( is.null(dfProf) || nrow(dfProf) == 0 ) {
      NULL
    } else {
      dfProf %>% 
        dplyr::group_by( TagType, Tag) %>% 
        dplyr::summarise( Score = sum(Score), .groups = "drop_last") %>% 
        dplyr::arrange(desc(Score)) %>% 
        dplyr::select( Score, TagType, Tag)
    }
  }
},
options = list(scrollX = "300px", scrollY = "300px", scroller = TRUE)
) 
```

Summary
=======================================================================

### Dimensions of the recommender matrix:

```{r}
renderText( dim(smrObj() %>% SMRMonTakeM) )
```

### Tag types and ranges:

```{r}
DT::renderDataTable( smrObj() %>% SMRMonTakeTagTypeRanges )
```


References
=======================================================================

#### In brief

- The Mathematica / WL datasets metadata was derived from the built-in function 
  [`ExampleData`](https://reference.wolfram.com/language/ref/ExampleData.html).

- The R datasets metadata was taken from [Rdatasets](https://vincentarelbundock.github.io/Rdatasets/) .

- The recommenders were made with the packages
  [`SMRMon-R`](https://github.com/antononcube/R-packages/tree/master/SMRMon-R)
  and
  [`LSAMon-R`](https://github.com/antononcube/R-packages/tree/master/LSAMon-R),
  [AAp1, AAp2, AAp3].

- The recommender interface is a slightly modified version of the generic flexdashboard in
  [`RecommenderDashboards`](https://github.com/antononcube/R-packages/tree/master/RecommenderDashboards),
  [AAp4].

#### Packages 

[AAp1] Anton Antonov,
[Sparse Matrix Recommender framework functions, R-package](https://github.com/antononcube/R-packages/tree/master/SparseMatrixRecommender),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp2] Anton Antonov,
[Sparse Matrix Recommender Monad, R-package](https://github.com/antononcube/R-packages/tree/master/SMRMon-R),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp3] Anton Antonov,
[Latent Semantic Analysis Monad, R-package](https://github.com/antononcube/R-packages/tree/master/LSAMon-R),
(2019),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).

[AAp4] Anton Antonov,
[Recommender Dashboarrds, R-package](https://github.com/antononcube/R-packages/tree/master/RecommenderDashboards),
(2021),
[R-packages at GitHub/antononcube](https://github.com/antononcube/R-packages).
