---
title: "Parsers for spoken dplyr commands"
author: Anton Antonov
date: "`r Sys.Date()`"
output: html_notebook
---

# Introduction

This notebook is to be used for demonstrations and explanations in the workshop:
["Conversational agents design and programming"](https://github.com/antononcube/ConversationalAgents/tree/master/Projects/DataScienceSalon-Miami-Nov-2018-Workshop)
to be given at 
[Data Science Salon MiamiNovember 6-7 2018](https://datascience.salon/miami11-18/).

# Getting some data

Here we load and use the data from the dplyr's tutorial: https://dplyr.tidyverse.org .

```{r}
# The easiest way to get dplyr is to install the whole tidyverse:
#install.packages("tidyverse")
library(dplyr)

starwars %>% 
  filter(species == "Droid")
```

# Parsing and interpretation functions


```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/antononcube/ConversationalAgents/24f02ece28ef130ff7b52430787b2d48c5118718/Projects/Spoken-dplyr-agent/R/Perl6-command-functions.R")
```

Change the directory names with the correct paths.
The paths below assume Mac OS X and the GitHub repository ConversationalAgents being 
in the current user directory.

```{r}
localUserDirName <- file.path( "/", "Users", Sys.info()["user"])
perl6ParsingLib <- file.path( localUserDirName, "ConversationalAgents", "Projects", "DataScienceSalon-Miami-Nov-2018-Workshop", "Code", "dplyrCommand") 
```


```{r}
DPLYRParse <- 
  function(cmd) { 
    Perl6Parse(command = cmd, 
           moduleDirectory = perl6ParsingLib, 
           moduleName = "DPLYRCommand",
           grammarClassName = "DPLYR-command",
           actionsClassName = NULL)
  }
```

```{r}
DPLYRInterpret <- 
  function(cmd) { 
    Perl6Parse(command = cmd, 
           moduleDirectory = perl6ParsingLib, 
           moduleName = "DPLYRCommand",
           grammarClassName = "DPLYR-command",
           actionsClassName = "DPLYR-command-actions")
  }
```

# Experiments

```{r}
DPLYRParse( "select the variable mass, height, hair_color")
```

```{r}
pipeline <-
  paste( DPLYRInterpret("load data"), 
         DPLYRInterpret("keep only the variables mass, height & hair_color"),
         DPLYRInterpret("mutate mass1 := mass, const <- 100"),
         DPLYRInterpret("group over mass1 & const"),
         DPLYRInterpret("find the counts"),
         DPLYRInterpret("arrange by n"),
         sep = " %>% ")
pipeline
```

```{r}
eval( parse( text = pipeline) )
```

