---
title: "Love food parsers"
author: Anton Antonov
date: "`r Sys.Date()`"
output: html_notebook
---

# Introduction

This notebook is to be used for demonstrations and explanations in the workshop:
["Conversational agents design and programming"](https://github.com/antononcube/ConversationalAgents/tree/master/Projects/DataScienceSalon-Miami-Nov-2018-Workshop)
to be given at 
[Data Science Salon MiamiNovember 6-7 2018](https://datascience.salon/miami11-18/).

# Load the FunctionalParsers package/code

```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/antononcube/MathematicaForPrediction/master/R/FunctionalParsers/FunctionalParsers.R")
```

# Programming the parsers

Here is a direct programming with functional parsers:

```{r}
pSUBJECT <- p.alt( c(p.symbol("i"), p.symbol("we"), p.symbol("you")))
pLOVE.VERB <- p.alt( c(p.symbol("love"), p.symbol("crave"), p.symbol("demand"), p.symbol("want"))) 
pLOVE.FOOD <- p.seq( c(pSUBJECT, pLOVE.VERB))
```

This might be considered as more clear:

```{r}
pSUBJECT <- p.symbol("i") %|% p.symbol("we") %|% p.symbol("you")
pLOVE.VERB <- p.symbol("love") %|% p.symbol("crave") %|% p.symbol("demand") %|% p.symbol("want")
pLOVE.FOOD <- pSUBJECT %&% pLOVE.VERB 
```

Let us proceed with rest of the definitions.

```{r}
pOBJECT <- p.symbol("sushi") %|% p.symbol("ice") %&% p.symbol("cream") %|% p.symbol("chocolate")
pOBJECTS <- p.symbol("sushi") %|% p.symbol("ice") %&% p.symbol("creams") %|% p.symbol("chocolates")
pOBJECTS <- p.symbol("sushi") %|% p.symbol("milks") %|% p.symbol("chocolates")
pINTEGER <- p.apply( as.integer, p.satisfy( function(x) grepl("^\\d.*$", x)) )
pOBJECTS.MULT <- pINTEGER %&% pOBJECTS
pOBJECT.LIST.ELEM <- pOBJECT %|% pOBJECTS %|% pOBJECTS.MULT
pOBJECT.LIST <- p.listof( p = pOBJECT.LIST.ELEM, sepParser = p.symbol("and") )
pOBJECT.SPEC <- p.shortest( pOBJECT.LIST.ELEM )
```

We have to redefine `pLOVE.FOOD` to take the last part of the sentense, the object specification:

```{r}
pLOVE.FOOD <- pSUBJECT %&% pLOVE.VERB %&% pOBJECT.SPEC
```


# Experiments


```{r}
code <- "we want 4 sushi"
tokens <- strsplit(code, split = "\\W")[[1]]
pLOVE.FOOD(tokens)
```

```{r}
ListToString( pLOVE.FOOD(tokens) )
```

